\Huge Conferences and the Price of Carbon

### 2019-05-28 main.tex
Telecon

\title{\Huge ACM and Climate Change}
\author{Benjamin C. Pierce (University of Pennsylvania) \\
Michael Hicks (University of Maryland) \\
Crista Lopes (University California, Irvine) \\
Jens Palsberg (University of California, Los Angeles)}

@@

This leads to a puzzle: How do we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  This seems an extremely difficult question to
answer: the harm and the compensating benefits cannot be directly
compared---they are apples and oranges.
%
Fortunately, there is a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything: the magic of markets.  By
mapping choices to currency amounts, markets facilitate individual valuation
of costs and benefits across vastly different activities.\bcp{Give a simple,
  concrete example.} For this reason, many policy experts advocate some form
of carbon pricing, which places a monetary cost on greenhouse gas emissions,
giving a market signal that changes aggregate behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
for lots of good phrasing and citations.}
Exactly what the
cost should be is a challenging question, but it has a clear ``success
criterion'': The cost should be set so that the world arrives at zero
emissions within the timeframe that climate scientists tell us is safe.

% (Experts seem to agree that the current price of around \$15 / ton is too
% low.)

Many countries and states (e.g., California) have already adopted carbon
pricing policies; more will follow.  The upshot is that, sooner or later,
carbon is going to be expensive.
\bcp{Yes, this may not happen.  But if it does not, we are probably
  screwed.  So might as well behave as if we knew it was going to happen.}
%
In the meantime, knowing that this is coming, what should we rationally (and
ethically) do now?

First, we should immediately start planning for how ACM, and computer-science
research more broadly, are going to continue to thrive in a world where air
travel is significantly more expensive.  Indeed, this may well involve
rethinking the whole basis of how computer science is done. 
\bcp{Add some meat to that.}

Second, we can begin gathering and analyzing data, to better understand both
the current carbon impact of our conferences and the likely effects (both
environmental and scientific) of potential changes in the way they are
organized.
\bcp{Put in the most interesting discussion and perhaps show an interesting
  diagram.}

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\item Moreover, offsets are an effective way to reduce carbon emissions {\em
  now}.  (Yes, there are bogus ones, but not all are bogus.)
\item Most importantly, it is the right thing to do: We should be changing
our behavior starting now, and giving ourselves a (correct) ``price signal''
is an effective way to achieve this.
\end{itemize}

The climate crisis is too large and too urgent to leave it to world leaders
to address at their own pace: organizations at every social scale should
confront their own contributions, raise awareness among their members, and
begin establishing new ways of doing business in the lower-carbon future
that is coming. For ACM, this especially means confronting the
carbon-intensive nature of our conferences.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does the rest of this smack of
  incrementalism?  Maybe delete it.  ``For example, ask the organizers of
  the conferences you attend what they are doing about reducing or
  offsetting emissions from participants' travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to
understand how to reduce its footprint now and prepare for the coming era of
expensive carbon.
\end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Think about adding headings, per Bishop's recommendation
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Change to a catchier title (``so something more personal such as
  "Your conference trip and climate change" might get more readers'') 
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}

>>>>

\title{\Huge Conferences and the Price of Carbon}
\author{Benjamin C. Pierce (University of Pennsylvania) \\
Michael Hicks (University of Maryland) \\
Crista Lopes (University California, Irvine) \\
Jens Palsberg (University of California, Los Angeles)}

@@

This leads to a puzzle: How do we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  This seems an extremely difficult question to
answer: the harm and the compensating benefits cannot be directly
compared---they are apples and oranges.
%
Fortunately, there is a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything: the magic of markets.  By
mapping choices to currency amounts, markets facilitate individual valuation
of costs and benefits across vastly different activities.\bcp{Give a simple,
  concrete example.} For this reason, many policy experts advocate some form
of carbon pricing, which places a monetary cost on greenhouse gas emissions,
giving a market signal that changes aggregate behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}
Exactly how this should be done is a challenging question, but it has a
clear success 
criterion: The cost should be set so that the world arrives at zero
emissions within the timeframe that climate scientists tell us is safe.
%
For ACM, this means that the carbon cost of conferences needs to be
reflected in their monetary cost.

Ultimately, this cost should be imposed from outside, by governments.
Indeed, many countries and states (e.g., California) have already adopted
carbon pricing policies; more will follow.
%
Moreover, although the current market price of carbon is still quite low
(around \$15 / ton), experts agree that this will need to rise significantly
over time to achieve the required effect.
%
Expecting that this is coming, what should we rationally do now to ensure
that ACM, and computer-science research broadly, continue to thrive in a
world where air travel is more expensive?  Believing that it needs to come
quickly, what should we ethically do now to accelerate the process?
Recognizing that the climate change is the defining crisis of our time, how
can ACM and its members participate in addressing it?

First, we can begin gathering and analyzing data, to better understand the
carbon footprint of our conferences and the likely effects (both
environmental and scientific) of potential changes in the way they are
organized.  \bcp{Put in the most interesting discussion and perhaps show an
  interesting diagram.}

% \bcp{Add some meat to that.
%   \begin{itemize}
%   \item List a few things we can do
%   \begin{itemize}
%   \item journalize conferences
%   \item go virtual
%   \item potential parts of a solution: regional conferences, virtual PC
%   meetings, virtual participation, mega-conferences
%   \end{itemize}
%   \item cite our report
%   \end{itemize}
% }

Second, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\item Moreover, offsets are an effective way to reduce carbon emissions {\em
  now}.  (Yes, there are bogus ones, but not all are bogus.)
\item Most importantly, it is the right thing to do: We should be changing
our behavior starting now, and giving ourselves a (correct) ``price signal''
is an effective way to achieve this.
\end{itemize}

Ultimately, responding to the inevitability of expensive carbon may well
involve rethinking the whole basis of how computer science is done.
\bcp{Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.}

The climate crisis is too large and too urgent to leave it to world leaders
to address at their own pace: organizations at every social scale should
confront their own contributions, raise awareness among their members, and
begin establishing new ways of doing business in the lower-carbon future
that is coming. For ACM, this especially means confronting the
carbon-intensive nature of our conferences.
% %
% You can help accelerate this process in a number of ways: 
% \begin{itemize}
% \item {\bf Get involved} in raising awareness about this issue in the
% organizations you are a part of.  \bcp{Does the rest of this smack of
%   incrementalism?  Maybe delete it.  ``For example, ask the organizers of
%   the conferences you attend what they are doing about reducing or
%   offsetting emissions from participants' travel.''}
% \item {\bf Connect} with others that are engaging with these issues---in
% your workplace, in your other communities, and within ACM (e.g., on the
% {\tt acm-climate} mailing list~\cite{acm-climate}).
% \item {\bf Analyze} your organization's carbon-emitting activities to
% understand how to reduce its footprint now and prepare for the coming era of
% expensive carbon.
% \end{itemize}

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Think about adding headings, per Bishop's recommendation
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \ite Find a place for this: {\tt acm-climate} mailing list~\cite{acm-climate}
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}
